Evaluating the Influence of Education on Current Unemployment Trends

### 2024-04-05 paper/paper.qmd
small grammar mistake fixed
updated paper

In recent years, the narrative surrounding employment and the value of higher education has become increasingly complex. Amidst a landscape marked by technological advancements and a globalizing economy, stories of job seekers with advanced degrees facing employment challenges have proliferated. There are even "trends" going around social media on platforms such as TikTok or Instagram, where people are sharing their experience of graduating with a degree, in some cases multiple degrees, and still struggling to find a job or a job that they perceive their degree to be worth (i.e. working as a barista at Starbucks when they have a computer science degree, etc.). News reports often depict long queues for scarce job openings, painting a vivid picture of the competitive and sometimes disheartening job market. This can be seen from news sources such as the `Toronto Sun` (@citesource9), the `blogTO` (@citesource8), and many more. This juxtaposition of high educational attainment and employment difficulty raises critical questions about the evolving dynamics of the labor market, the role of education, and the implications for future workforce development.

@@

- **Physical Presence**: Jobs that require a physical presence as mentioned before are less likely to be replaced by AI. For instance, it is difficult for AI to replace people such as plumbers firefighters or people working in trades.

>>>>

In recent years, the narrative surrounding employment and the value of higher education has become increasingly complex. Amidst a landscape marked by technological advancements and a globalizing economy, stories of job seekers with advanced degrees facing employment challenges have proliferated. There are even "trends" going around social media on platforms such as TikTok or Instagram, where people are sharing their experience of graduating with a degree, in some cases multiple degrees, and still struggling to find a job or a job that they perceive their degree to be worth (i.e. working as a barista at Starbucks when they have a computer science degree, etc.). News reports often depict long queues for scarce job openings, painting a vivid picture of the competitive and sometimes disheartening job market. This can be seen from news sources such as the `Toronto Sun` (@citesource9), the `blogTO` (@citesource8), and many more showcasing huge line ups for LCBO and a grocery store respectively. This juxtaposition of high educational attainment and employment difficulty raises critical questions about the evolving dynamics of the labor market, the role of education, and the implications for future workforce development.

@@

- **Physical Presence**: Jobs that require a physical presence as mentioned before are less likely to be replaced by AI. For instance, it is difficult for AI to replace people such as plumbers, firefighters or people working in trades.
